---
title: "Lab 1 - Data visualization"
author: "Dennis Park"
format: pdf
editor: visual
---

## Load Packages

```{r, warning = FALSE}
#| label: load-packages
#| message: false

library(tidyverse)
library(viridis)
```

## Exercise 1

(Type your answer to Exercise 1 here. Add code chunks as needed. Don't forget to label your code chunk. Do not use spaces in code chunk labels.)

```{r}
ggplot(data = midwest,
       aes(x = popdensity)) +
  geom_histogram(binwidth = 10000)
```

The shape is skewed right, and there are outliers as there extreme data represented on the right side.

## Exercise 2

(Type your answer to Exercise 2 here. Add code chunks as needed. Don't forget to label your code chunk. Do not use spaces in code chunk labels.)

```{r}
ggplot(data = midwest,
       aes(x=percollege, y =percbelowpoverty, color = state)) +
  geom_point() +
  labs(x = "percent with degree",
       y ="percent below poverty",
       title = "Degree vs poverty") +
  scale_color_viridis_d()
```

## Exercise 3

(Type your answer to Exercise 3 here. Add code chunks as needed. Don't forget to label your code chunk. Do not use spaces in code chunk labels.)

In most states, there is a great number of data points where both percent below poverty and percent with degree is between 10-30. The states have a similar overall shape of data but states like OH and IL have some extreme points of data.

## Exercise 4

```{r}
ggplot(data = midwest,
       aes(x=percollege, y =percbelowpoverty, color = state))+
  geom_point() +
  labs(x = "percent with degree",
       y ="percent below poverty",
       title = "Degree vs poverty")+
  scale_color_viridis_d()+
  facet_wrap("state")+
  geom_smooth(se=FALSE)


```

I prefer this plot instead of Ex 2 because you can focus on each individual state better. You are able to compare them side by side and with the geom_smooth function, you can see the direction of the data.

## Exercise 5

```{r}
ggplot(data = midwest,
       aes(x=area, y =state, color = state))+
  geom_boxplot() +
  labs(x = "area",
       y ="state",
       title = "Area vs State")
```

## Exercise 6

## Exercise 7
